A minimal reaction-diffusion neural model generates {\emph{C. elegans}} undulation

### 2020-12-25 paper.tex
Some changes made to captions, fixes, etc

@@

% TODO:
% - decide whether to cite CPG
% - italicise C. elegans
The purpose of this paper is to describe a minimal, biomimetic, reaction-diffusion model for the \emph{C. elegans} central pattern generator (CPG) \citep{xu2018, wen2012}.  We use simulation methods to show that a small network of \citet{fitzhugh1955}-\citet{nagumo1962} neurons (one of the simplest neuronal models) based on a skeleton model of the C. elegans CPG can reproduce key features of C. elegans undulation \citep{magnes2012} and thus locomotion.

@@

\begin{figure}[h!]
    \label{fig: xu_cpg}
    \centering
    \includegraphics[width=9cm]{figures/xu_cpg/xu_cpg.png}
    \caption{The central pattern generator proposed by \citet{xu2018}.  Note the structure of the neurons, especially the head oscillator driving the descending pathway.}
\end{figure}

@@

\begin{figure}[h!]
    \ContinuedFloat
    \centering
    \inputtikz{figures/cpg/cpg}
    \label{fig: cpg}
    \caption{Our simplified central pattern generator model.  Descending coupling (shows inhibitory connections, and potential flows through gap junctions, not necessarily symmetric)}
\end{figure} % TODO: legend

@@

@@

The CPG network which we created is of the same form as the 2-D musculature of our simulated worm.  Each neuron is attached to a muscle; when it fires, it causes the attached muscle to contract.​  We model the muscles as leaky integrators of the neuron's voltage; therefore, Gaussian smoothing of the neuron's voltage works to ``create'' an effective muscle contraction signal.  Through Gaussian smoothing, the movement is heavily dependent on the current state of the neuron but also dependent somewhat on the history. ​

Much like \citet{izquierdo2018} did, we take a segment-based approach to the worm model.  Pairs of muscles on either side determine the overall angular displacement per segment.​  The magnitude of the “contraction” resulting from the smoothing is interpreted as an angular displacement for that segment.​  We use a cubic spline interpolation to smoothen the worm body.

Each neuron is assumed to be connected to a muscle; when it fires, it should cause that muscle to contract.​
Pairs of neurons on either side determine the overall angular displacement per segment.​
Gaussian smoothing and a cubic spline are used to mimic muscle movement and medium resistance.​
The magnitude of the “contraction” resulting from the smoothing is interpreted as an angular displacement for that segment.​

@@

% The circuit in \Fref{fig: nagumo_ckt} is an analog solver for the FitzHugh-Nagumo equations.  Namely, the

@@

However, this is only one neuron.  In order to implement a full central pattern generator, we implemented diffusive coupling mechanisms.  These mechanisms are shown in \Fref{fig: coupling_ckt}.  We implemented a positive diffusion coefficient by passing the voltage through a resistor (to simulate $D$), and then a diode (to simulate $\mathrm{max}(\Delta v, 0)$).  The negative diffusion coefficient was implemented by using an inverting amplifier with a small gain, and then passing through a diode.
\newsavebox{\tempbox}
\begin{figure}
    \centering
    \inputtikz{figures/coupling/coupling}
    \caption{Coupling methods}
    \label{fig: coupling}
\end{figure}

>>>>

\author[2]{Susannah Zhang}

@@

The purpose of this paper is to describe a minimal, biomimetic, reaction-diffusion model for the \emph{C. elegans} central pattern generator (CPG) \citep{xu2018, wen2012}.  We use simulation methods to show that a small network of \citet{fitzhugh1955}-\citet{nagumo1962} neurons (one of the simplest neuronal models) based on a skeleton model of the C. elegans CPG can reproduce key features of C. elegans undulation \citep{magnes2012} and thus locomotion.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=9cm]{figures/xu_cpg/xu_cpg.png}
    \caption{The central pattern generator proposed by \citet{xu2018}.  Note the structure of the neurons, especially the head oscillator driving the descending pathway.}
    \label{fig: xu_cpg}
\end{figure}

@@

\begin{figure}[h!]
    \ContinuedFloat
    \centering
    \inputtikz{figures/cpg/cpg}
    \caption{Our simplified central pattern generator model.  Descending coupling (shows inhibitory connections, and potential flows through gap junctions, not necessarily symmetric)}
    \label{fig: cpg}
\end{figure} % TODO: legend

@@

Essentially, the way the code works is that the main function calculates the left-hand side of the system of differential equations which is materialized from our CPG connectome, when given the state and a set of unchanging parameters.  This is then run through an ODE solver which solves the trajectory of the system given some initial conditions (for example, if the neuron does not initially fire, for example, the system may remain in a steady state and not oscillate).

@@

The CPG network which we created is of the same form as the 2-D musculature of our simulated worm.  Each neuron is attached to a muscle; when it fires, it causes the attached muscle to contract.  We model the muscles as leaky integrators of the neuron's voltage; therefore, Gaussian smoothing of the neuron's voltage works to ``create'' an effective muscle contraction signal.  Through Gaussian smoothing, the movement is heavily dependent on the current state of the neuron but also dependent somewhat on the history.

Much like \citet{izquierdo2018} did, we take a segment-based approach to the worm model.  Pairs of muscles on either side determine the overall angular displacement per segment.  The magnitude of the “contraction” resulting from the smoothing is interpreted as an angular displacement for that segment.  We use a cubic spline interpolation to smoothen the worm body.

Each neuron is assumed to be connected to a muscle; when it fires, it should cause that muscle to contract.
Pairs of neurons on either side determine the overall angular displacement per segment.
Gaussian smoothing and a cubic spline are used to mimic muscle movement and medium resistance.
The magnitude of the “contraction” resulting from the smoothing is interpreted as an angular displacement for that segment.

@@

@@

However, this is only one neuron.  In order to implement a full central pattern generator, we implemented diffusive coupling mechanisms.  These mechanisms are shown in \Fref{fig: coupling}.  We implemented a positive diffusion coefficient by passing the voltage through a resistor (to simulate $D$), and then a diode (to simulate $\mathrm{max}(\Delta v, 0)$).  The negative diffusion coefficient was implemented by using an inverting amplifier with a small gain, and then passing through a diode.
\newsavebox{\tempbox}
\begin{figure}
    \centering
    \inputtikz{figures/coupling/coupling}
    \caption{Coupling methods}
    \label{fig: coupling}
\end{figure}
